### 2021-01-10 tex/paper.tex
Rewrite abstract.

In this paper we present a survey conducted by comparing low-code tools with model-driven tools for developing software in order to get a better understanding of the advantages and drawbacks of both approaches and whether they are a viable alternative to traditional software development.

>>>>

In this paper we present a survey conducted by evaluating various low-code tools in order to get a better understanding of the advantages and drawbacks. The evaluation entails creating a test application with each low-code tools and assessing factors such as ease of use and scalability. Using the results from this evaluation, we try to determine if and when low-code platforms are a viable alternative or even preferable to traditional software development using a model-driven architecture.
